Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-04-11 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
more planning/outline,updates to results section, figure captions

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency. In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution. Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and  how NEI may affect hot emission measure slopes.
	\par\autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases as well as the equivalent single-fluid cases. In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot and cool emission measure slopes and the nanoflare heating model. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	\par 1D hydrodynamic models are excellent tools for computing field-aligned quantities in coronal loops. However, because of the small cell sizes needed to resolve the transition region and consequently small timesteps demanded by thermal conduction, the use of such models in large parameter space explorations is made impractical by long computational runtimes \citep{bradshaw_influence_2013}. We use the popular 0D enthalpy-based thermal evolution of loops (EBTEL) model \citep{klimchuk_highly_2008,cargill_enthalpy-based_2012,cargill_enthalpy-based_2012-1,cargill_modelling_2015}. This model, which has been successfully benchmarked against the 1D hydrodynamic HYDRAD code of \citet{bradshaw_influence_2013}, computes, with very low computational overhead, time-dependent, spatially-averaged loop quantities.

@@

	where $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. A full discrussion and derivation of these 0D two-fluid equations can be found in the appendix of \citetalias{barnes_inference_2016}.
	\par\hl{Include some temperature and density profiles for nanoflare trains in here somehow? May need to move to next section...}

@@

	\par\hl{Details about static parameters for all runs.} All events are modeled as triangular pulses of fixed duration $\tau=200$ s.

@@

		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions. \hl{Adjust depending on what value of $\beta$ we use in the end.	}}

@@

	\par Determining the heating frequency in AR cores will help to place constraints on the source(s) of heat in the corona. We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s. Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $\varepsilon_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.

@@

	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1,2$ such that the event energy scales either linearly or quadratically with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large. Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.

@@

	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$. For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. We do not attempt to apply an advanced forward modeling treatment here and instead reserve such an approach for a future paper. However, while effects due to NEI are neglected in our parameter space exploration, in \autoref{subsec:non-eq_ion} we consider the emission measure due to $T_{eff}$, the effective temperature due to NEI, for several test cases in order to diagnose how this might affect our calculated emission measure slopes.

@@

	\par For each species, type of power-law heating function, and waiting time $t_N$, $N_{R}$ emission measure curves are calculated. Because drawing event amplitudes from a power-law distribution introduces random fluctuations into our model, we must be sure to account for the full range of effects due to the distribution. This is especially true in the low-frequency regime, when $T_N\ge\tau_{cool}$, the cooling timescale, and there are fewer events per run. In this case, one or two especially strong heating events can lead to an extremely enhanced hotward emission measure; conversely, a run with only small events will lead to a diminished hotward slope. Thus, the mean $\mathrm{EM}$ curve of each set of $N_{R}$ runs can be said to reasonably represent the expected hot emission for a given $t_N$.

@@

	\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak. To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$. Contrastingly, past studies of hot emission are less abundant; thus, the ``hot'' region where the $\mathrm{EM}$ is thought to follow a power-law is far less constrained. In order to best describe the steepness of the emission measure hotward of the peak, we choose to fit $\mathrm{EM}$ between the temperatures at which the emission measure is $99\%$ and $92\%$ of the peak value. We have no physical reason for choosing these particular bounds, but note that on this interval, the mean hotward emission is reasonably well-described by a power-law relationship. Fitting too close to the wide peak leads to misleadingly shallow slopes while fitting too close to the steep drop near $\log{T}\sim7.5$ results in steep slopes not particularly representative of the hotward emission. We perform the fit using the Levenberg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.

@@

		\caption{EM grids will go here, electron heating}

@@

		\caption{EM grids will go here, ion heating}

@@

@@

		\caption{\hl{Maybe single EM grid will go here}}

@@

@@

	%\subsection{Full Parameter Space Comparison}
	%\label{subsec:all_params}
		\caption{\hl{Put EM ratio histograms here, maybe include hot slope histograms somewhere too}}
			\label{fig:histos}

>>>>

	\par In our first paper, \citet{barnes_inference_2016} \citepalias[hereafter]{barnes_inference_2016}, we studied the effect of pulse duration, flux limiting, and NEI on hot emission from single nanoflares. In this second paper in our series on hot emission in AR cores, we use an efficient two-fluid hydrodynamic model to explore the effect of repeated impulsive heating events of varying frequency on the resulting emission measure distribution. In particular, we look at how the hot emission is affected by heating preferentially the electrons or the ions with events drawn from a power-law distribution versus uniform heating rates. Additionally, we consider the effect of scaling the inter-event waiting time to the event energy and how NEI may affect hot emission measure slopes. We use an emission measure ratio, similar to that of \citet{brosius_pervasive_2014} to assess the relative importance of hot emission over the entire range of power-law indices and heating frequencies. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure curves and slopes for the electron and ion heating cases \st{as well as the equivalent single-fluid cases}. In \autoref{sec:discussion}, we discuss the implications of two-fluid effects in the context of hot \st{and cool} emission measure slopes and the nanoflare heating model. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	\par 1D hydrodynamic models are excellent tools for computing field-aligned quantities in coronal loops. However, because of the small cell sizes needed to resolve the transition region and consequently small timesteps demanded by thermal conduction, the use of such models in large parameter space explorations is made impractical by long computational runtimes \citep{bradshaw_influence_2013}. We use the popular 0D enthalpy-based thermal evolution of loops (EBTEL) model \citep{klimchuk_highly_2008,cargill_enthalpy-based_2012,cargill_enthalpy-based_2012-1,cargill_modelling_2015} in order to efficiently simulate the evolution of a coronal loop over a large parameter space. This model, which has been successfully benchmarked against the 1D hydrodynamic HYDRAD code of \citet{bradshaw_influence_2013}, computes, with very low computational overhead, time-dependent, spatially-averaged loop quantities.

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.

@@

@@

		\caption{Total Parameter space covered. $\Sigma$ indicates the species that is heated, where ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions. \hl{Are we going to look at the single-fluid case? If not, remove if here and reconsider total number of heating functions.}}

@@

	\par Determining the heating frequency in AR cores will help to place constraints on the source(s) of heat in the corona. We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s and $\tau=200$ s. Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $\varepsilon_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.

@@

	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large. Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (electron or ion ), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$).

@@

	\par In our 0D model, the emission measure is calculated using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$. For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at iteration $i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. Furthermore, for each of the $N_R$ runs per $t_N$ value, we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	%\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak. To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$. Contrastingly, past studies of hot emission are less abundant; thus, the ``hot'' region where the $\mathrm{EM}$ is thought to follow a power-law is far less constrained. In order to best describe the steepness of the emission measure hotward of the peak, we choose to fit $\mathrm{EM}$ between the temperatures at which the emission measure is $99\%$ and $92\%$ of the peak value. We have no physical reason for choosing these particular bounds, but note that on this interval, the mean hotward emission is reasonably well-described by a power-law relationship. Fitting too close to the wide peak leads to misleadingly shallow slopes while fitting too close to the steep drop near $\log{T}\sim7.5$ results in steep slopes not particularly representative of the hotward emission. We perform the fit using the Levenberg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.

@@

		\includegraphics[width=2\columnwidth]{figures/em_grid_electron_a25.pdf}
		\caption{Emission measure distributions for varying waiting-times, $t_N$ in the case where only the electrons are heated. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (blue). The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

		\includegraphics[width=2\columnwidth]{figures/em_grid_ion_a25.pdf}
		\caption{Same as \autoref{fig:el_em}, but for the case where only the ions are heated.}

@@

		\includegraphics[width=2\columnwidth]{figures/nT_sample_curves_tn1500_electron.pdf}
		\caption{Example temperature and density profiles for an intermediate heating frequency, $t_N=1500$ s for several different heating function types.}

@@

		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T0.pdf}
		}
		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T0.pdf}
		}
		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair}

@@

		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T0.pdf}
		}
		\subfigure[]{%
		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T0.pdf}
		}

@@
